---
title: "Confluence Crew Dynamic report"

params:
  n: NA 
  
output: html_document


---
```{r data_setup, message=FALSE, warning=FALSE, include=FALSE}
library(flextable)
library(reactable)
library(pander)
library(knitr)
library(forcats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(stringr)
library(tools)
library(readr)
library(anytime)
library(data.table)
library(here)
library(tinytex)
library(gt)
library(kableExtra)
library(scales)
library(pander)
library(ggthemes)
library(pals)
library(plotly)
here()

#set up color palette for graphs
colors <- unname(glasbey())

### CREATING DATAFRAME ###
#when running in RStudio use:
ccdata <- read.csv(here("data", "Confluence_Crew_Clean_Data.csv"))

ccdata$Datetime <- mdy_hms(ccdata$Datetime)


ccdata <- mutate(ccdata, Station=recode(Station,
                                      "PC04.38" = "Paradise Creek (PC04.38)",
                                       "ROSC00.80" = "Rose Creek (ROSC00.80)",
                                       "SFPR12.50" ="South Fork Palouse River (SFPR12.50)",
                                       "SFPR22.37" = "South Fork Palouse River (SFPR22.37)",
                                       "SFPR23.38" = "South Fork Palouse River (SFPR23.38)",
                                       "SFPR23.89" = "South Fork Palouse River (SFPR23.89)",
                                       "SFPR24.27" = "South Fork Palouse River (SFPR24.27)",
                                       "UFC40.72" = "Union Flat Creek (UFC40.72)",
                                       "UFC42.03" = "Union Flat Creek (UFC42.03)",
                                       "UNTRIB-FMC03.33" = "Unnamed Tributary Four Mile Creek (UNTRIB-FMC03.33)",
                                       "UNTRIB-UFC0.12" = "Unnamed Tributary Union Flat Creek (UNTRIB-UFC0.12)"))

n = params

if(n == "PC04.38"){
  Station = ccdata[ccdata$Station == "Paradise Creek (PC04.38)", ]
}

if(n == "ROSC00.80"){
  Station = ccdata[ccdata$Station == "South Fork Palouse River (SFPR12.50)", ]
}

```

# `r n` Report

This is a summary of Confluence Crew site data containing data from water quality samples collected monthly at `r n`. Several figures have been generated below to show the trends in water quality parameters throughout the sampling period. For more information, please contact Tal Atkins at americorps4@palousecd.org. 

### **Air Temperature** 

The figure below displays air temperature ($^\circ$C), measured monthly in the field using a thermometer.

```{r airtemperature_graph, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=12}

#set up temporary file
TEMP = subset(Station, Parameter == "Air Temperature Average (C)")

TEMP_PLOT = ggplot() + geom_line(aes(y = Value, x = Datetime), data = TEMP) + 
  ylab("Air Temperature (C)")+
  xlab("")+
  theme_solarized_2(light = TRUE, base_size = 20)+
  theme(legend.position = "right", panel.grid.minor.x = element_blank())+
  theme(panel.border = element_rect(colour = "black", fill=NA, size=2))+
  scale_color_manual(values = colors)+
  #scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y")+
  theme(axis.text.x=element_text(angle=60, hjust=1))


TEMP_PLOT


```
